Factors affecting health sector expenditure in OECD countries

### 2025-02-21 products/manuscript/Manuscript.qmd
changes to rendered files
work #2

The structure below is one possible setup for a manuscript, or a general data analysis project (including the course project). Adjust as needed. 
You don't need to have exactly these sections, but the content covering those sections should be addressed.

@@

```{r, echo=FALSE, message=FALSE}
# load a few R packages
library(here)
library(knitr)
library(here)
library(readxl)
```

@@

## Data import and cleaning
```{r}
file_path <- here("data","raw-data", "wdi-oecd.xlsx")
data <- read_excel(file_path, sheet="Data")
```

## Statistical analysis

@@

## Schematic of workflow

Sometimes you might want to show a schematic diagram/figure that was not created with code (if you can do it with code, do it). @fig-schematic is an example of some - completely random/unrelated - schematic that was generated with Biorender.
We store those figures in the `assets` folder.

```{r}
#| label: fig-schematic
#| fig-cap: "A figure that is manually generated and shows some overview/schematic. This has nothing to do with the data, it's just a random one from one of our projects I found and placed here."
#| echo: FALSE
knitr::include_graphics(here("assets","antigen-recognition.png"))
```

@@

@tbl-summarytable shows a summary of the data.

Note the loading of the data providing a **relative** path using the `../../` notation. (Two dots means a folder up). You never want to specify an **absolute** path like `C:\ahandel\myproject\results\` because if you share this with someone, it won't work for them since they don't have that path. You can also use the `here` R package to create paths. See examples of that below. I generally recommend the `here` package.

```{r}
#| label: tbl-summarytable
#| tbl-cap: "Data summary table."
#| echo: FALSE
resulttable=readRDS("../../results/tables/summarytable.rds")
knitr::kable(resulttable)
```

@@

_To get some further insight into your data, if reasonable you could compute simple statistics (e.g. simple models with 1 predictor) to look for associations between your outcome(s) and each individual predictor variable. Though note that unless you pre-specified the outcome and main exposure, any "p<0.05 means statistical significance" interpretation is not valid._

@fig-result shows a scatterplot figure produced by one of the R scripts.

```{r}
#| label: fig-result
#| fig-cap: "Height and weight stratified by gender."
#| echo: FALSE
knitr::include_graphics(here("results","figures","height-weight-stratified.png"))
```

@@

_Use one or several suitable statistical/machine learning methods to analyze your data and to produce meaningful figures, tables, etc. This might again be code that is best placed in one or several separate R scripts that need to be well documented. You want the code to produce figures and data ready for display as tables, and save those. Then you load them here._

Example @tbl-resulttable2 shows a summary of a linear model fit.

```{r}
#| label: tbl-resulttable2
#| tbl-cap: "Linear model fit table."
#| echo: FALSE
resulttable2 = readRDS(here("results","tables","resulttable2.rds"))
knitr::kable(resulttable2)
```

@@

## Summary and Interpretation
_Summarize what you did, what you found and what it means._

## Strengths and Limitations
_Discuss what you perceive as strengths and limitations of your analysis._

## Conclusions
_What are the main take-home messages?_

>>>>

@@

```{r, echo=FALSE, message=FALSE}
# load a few R packages
library(here)
library(knitr)
library(here)
library(readxl)
library(writexl)
```

@@

# Data import and cleaning
```{r}
file_path <- here("data","raw-data", "wdi-oecd.xlsx")
data <- read_excel(file_path, sheet="Data")
```

## A look into the original for of dataset

@@

# EDA based on clean dataset

## Descriptive Analysis

@@

### Looking into the trend for our possible dependent variable

@fig-health-expenditure-plot how "Health Expenditure as a Percentage of GDP Over Time (2010–2020)" is distributed over the years for top 5 OECD countries.

```{r}
#| label: fig-health-expenditure-plot
#| fig-cap: "Current Health Expenditure as a % of GDP (2010–2020): Top 5 nations"
#| echo: FALSE
knitr::include_graphics(here("results","figures","health_expenditure_plot.png"))
```

@fig-health-exp-aus how "Health Expenditure as a Percentage of GDP changes over time for Australia.

```{r}
#| label: fig-health-exp-aus
#| fig-cap: "Health Expenditure (% of GDP), Country: Australia"
#| echo: FALSE
knitr::include_graphics(here("results", "figures", "health_exp_aus.png"))
```

@fig-pop-growth-aus checks if Health Expenditure as a Percentage of GDP over the Years shows any reation with annual population growth for Australia.

```{r}
#| label: fig-pop-growth-aus
#| fig-cap: "Health Expenditure (% of GDP), Country: Australia"
#| echo: FALSE
knitr::include_graphics(here("results","figures","pop_growth_aus.png"))
```

@fig-he_per_capita checks if Health Expenditure Per Capita (USD) over the Years shows any reation with annual population growth for Australia.

```{r}
#| label: fig-he_per_capita
#| fig-cap: "Health Expenditure Per Capita (USD, Country: Australia"
#| echo: FALSE
knitr::include_graphics(here("results","figures","health_exp_per_capita_aus.png"))
```

@@

@@

_To be added._

@@

## Summary and Interpretation
_To be added._

## Strengths and Limitations
_To be added._

## Conclusions
_To be added._
